% Created 2022-11-11 Fri 20:55
% Intended LaTeX compiler: pdflatex
\documentclass{scrartcl}
  \renewcommand\sectionformat{\llap{\thesection\autodot\enskip}}
  \renewcommand\subsectionformat{\llap{\thesubsection\autodot\enskip}}
  \renewcommand\subsubsectionformat{\llap{\thesubsubsection\autodot\enskip}}
  
\usepackage[utf8]{inputenc}
\usepackage[T1,T2A]{fontenc}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage[american]{babel}
% features: (embed-files custom-font microtype acronym par-sep alegreya-typeface)

  \usepackage[main,include]{embedall}
  \IfFileExists{./\jobname.org}{\embedfile[desc=The original file]{\jobname.org}}{}
  
\usepackage{AlegreyaSans}
\usepackage[scale=0.88]{sourcecodepro}

\usepackage[activate={true,nocompatibility},final,tracking=true,kerning=true,spacing=true,factor=2000]{microtype}

\newcommand{\acr}[1]{\protect\textls*[110]{\scshape #1}}
\newcommand{\acrs}{\protect\scalebox{.91}[.84]{\hspace{0.15ex}s}}
\setlength{\parskip}{\baselineskip}
\setlength{\parindent}{0pt}

% end features
\date{\today}
\title{Notes}

  \providecolor{url}{HTML}{0077bb}
  \providecolor{link}{HTML}{882255}
  \providecolor{cite}{HTML}{999933}
  \hypersetup{
    pdfauthor={},
    pdftitle={Notes},
    pdfkeywords={},
    pdfsubject={},
    pdfcreator={Emacs 28.2 (Org mode 9.6)},
    pdflang={English},
    breaklinks=true,
    colorlinks=true,
    linkcolor=link,
    urlcolor=url,
    citecolor=cite
}
  \urlstyle{same}
  \begin{document}

\maketitle
\tableofcontents \clearpage
\section{Introduction}
\label{sec:org78b2e43}
Personal notes on my part of project. That includes logic, \acr{api}, and notes on \texttt{Pixi JS} I'm going to be using
\section{Pixi}
\label{sec:org43ba986}
\subsection{Display tree}
\label{sec:orgb1e3814}
It all begins with \verb~Stage~. Which is created by \verb~Application~, but I'm going to be redefining that. Then tree of
\verb~Container~, with leaves being \verb~Sprite~. For performance it's possible to use \verb~Particle Container~ but it has
restrictions on sprites (must come from same texture), can't use filters and masks. None of these are restricting
graphics it seems.
\subsubsection{Graphics}
\label{sec:org410be69}
Inherits from \verb~Container~ (a pity).

Most of my work will be done here.

!! Don't try to \texttt{clear()} and then redraw \texttt{Graphics} every frame. You should ideally draw them once and transform
   resulting object

\subsubsection{Context}
\label{sec:org43a0b63}
If a method is passed as parameter, when parameter is called, \texttt{this} is the object calling the function, not object for
which the method was written. To fix, \texttt{.bind(this)}.
\end{document}